\herschel\footnote{{\it Herschel} is an ESA space observatory with science instruments provided by European-led Principal Investigator consortia and with important participation from NASA.} Orion Protostar Survey (HOPS) Imaging and Photometry Results.

### 2017-10-19 HOPS/photometry/ms.tex
submitted version

\subsection{Population differences}
\label{sec:popdiff}
\par
We also consider the implications if the correlations shown in Figure~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec} are due to systematic differences in the observed population as a function of sub-region.  \cite{ali} show that \herschel\ colors become redder with increasing envelope mass (envelope accretion rate).  In fact, the envelope infall rate is the dominating factor in setting colors.  We rule out inclination as a factor because no reasonable justification can be made for systematic differences in inclination as a function of sub-region in Orion.  Thus, we focus on differences in envelope properties.  When interpreted as such, Figures~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec}  imply that either the accretion process is different amongst the sub-regions, or that the protostars are at systematically different stages of development in each sub-region.   Both scenarios thereby conspire to lead to systematic differences in the envelope properties of the protostars.
\par
If we surmise that the accretion process is the leading cause, then there are two means to achieve this end: (i) the available gas and dust contributing to the envelope is systematically different between the sub-regions, or (ii) the central cores are systematically more massive in regions with redder colors.  Both scenarios may, in fact, point to simply having higher gas+dust densities and higher gas+dust content to explain redder colors.  We conclude that the observed properties of \herschel-detected protostars in Orion are consistent with predicted differences in populations implied by differences in gas column densities and star-formation scenarios in the region.
\par
Megeath et al (TOM, what reference goes here?) argue that regions with higher density may speed up protostellar evolution because collapse time-scales are dependent on the local density of material.  Thus, the observed trends in Figures~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec} may alternatively be viewed as differences in the evolutionary status of the protostars.  To explain the trend, the protostars in the Orion OMC-2/3 and ONC sub-regions are required to have transferred more of their mass in the central cores, which leads to more accretion and higher infall rates.  While similar to differences in the accretion processes, this scenarios suggests a fundamental difference in the star-formation process itself between sub-regions.

>>>>

\subsection{Population differences}
\label{sec:popdiff}
\par
We also consider the implications if the correlations shown in Figure~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec} are due to systematic differences in the observed population as a function of sub-region.  \cite{ali} show that \herschel\ colors become redder with increasing envelope mass (envelope accretion rate).  In fact, the envelope infall rate is the dominating factor in setting colors.  We rule out inclination as a factor because no reasonable justification can be made for systematic differences in inclination as a function of sub-region in Orion.  Thus, we focus on differences in envelope properties.  When interpreted as such, Figures~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec}  imply that either the accretion process is different amongst the sub-regions, or that the protostars are at systematically different stages of development in each sub-region.   Both scenarios thereby conspire to lead to systematic differences in the envelope properties of the protostars.
\par
If we surmise that the accretion process is the leading cause, then there are two means to achieve this end: (i) the available gas and dust contributing to the envelope is systematically different between the sub-regions, or (ii) the central cores are systematically more massive in regions with redder colors.  Both scenarios may, in fact, point to simply having higher gas+dust densities and higher gas+dust content to explain redder colors.  We conclude that the observed properties of \herschel-detected protostars in Orion are consistent with predicted differences in populations implied by differences in gas column densities and star-formation scenarios in the region.
\par
Alternatively, regions with higher density may speed up protostellar evolution because collapse time-scales are dependent on the local density of material.  Thus, the observed trends in Figures~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec} may be viewed as differences in the evolutionary status of the protostars.  To explain the trend, the protostars in the Orion OMC-2/3 and ONC sub-regions are required to have transferred more of their mass in the central cores, which leads to more accretion and higher infall rates.  While similar to differences in the accretion processes, this scenarios suggests a fundamental difference in the star-formation process itself between sub-regions.
